Eco Tracker Appendix

### 2025-03-27 paper/appendix.tex
add some notes to the appendix

\section{Simple Battery Drain Baseline}
An initial experiment to verify that an agent is capable of learning involved a simple battery drain test.
The purpose was to check the agents' ability to learna long-term strategy.
It is simple enough to take early rewards, but in a battery drain test, the agent must learn to balance short-term rewards with long-term goals and conserve energy.
The battery was fully charged and the agent was run for as long as needed to discharge the battery while trying to maximize message collection/transmission.
The power was discretized into 400 power levels, the day was divided into 48 time steps, and the maxmimum message queue size was 5 messages and ran for 6 days until the battery was drained.

@@

The reward shaping optimization resulted in an agent with a maximum message count of 253.
The agent was able to learn a long-term strategy and was able to balance short-term rewards with long-term goals.
The agent appears to need intermediate rewards to learn a long-term strategy.
The following parameters were found: power reward =0.000, Action0=-1.17324902,Action1=-0.463915495, Action2=-2, PerMessage=	0.602358605

It is interesting that the reward shaping produced a better result than pure message count.
The reward shaping shows the agent which actions should be rewarded to produce a better message count.
This is likely because the gradient of rewards did not provide enough information to the agent to learn a long-term strategy for the hyper parameter tuning case.

>>>>

\section{Simple Battery Drain Baseline}
An initial experiment to verify that an agent is capable of learning involved a simple battery drain test.
The purpose was to check the agents' ability to learn a long-term strategy.
It is simple enough to take early rewards, but in a battery drain test, the agent must learn to balance short-term rewards with long-term goals and conserve energy.
The battery was fully charged and the agent was run for as long as needed to discharge the battery while trying to maximize message collection/transmission.
The power was discretized into 400 power levels, the day was divided into 48 time steps, and the maximum message queue size was 5 messages and ran for 6 days until the battery was drained.

@@

The reward shaping optimization resulted in an agent with a maximum message count of 253 or 252 depending on which seed is selected.
The optimization found reward values that the agent used to come up with a strategy that happens to outperform all baselines.
The agent appears to need intermediate rewards to learn a long-term strategy.
The following parameters were found: power reward =0.000, Action0=-1.17324902,Action1=-0.463915495, Action2=-2, PerMessage=	0.602358605
The agent is able to outperform the baseline because the baseline runs out of power with a full message queue and never gets to send the message.

It is interesting that the reward shaping produced a better result than pure message count.
The reward shaping shows the agent which actions should be rewarded to produce a better message count.
This is likely because the gradient of rewards did not provide enough information to the agent to learn a long-term strategy for the hyper parameter tuning case.
This methodology isn't amazing, because we pretty much guide the agent every step of the way by giving rewards for certain actions, rather than outcomes. 
A different approach is likely necessary to ensure that the prcess is more robust.
